---
title: "Lab03 - F tests for ANOVA"
subtitle: "STAT 242: Intermediate Statistics"
output: pdf_document
---

## Goals

The goal in this lab is to practice F tests for ANOVA.

## Loading packages

Here are some packages with functionality you may need for this lab.  Run this code chunk now.

```{r}
library(readr)
library(ggplot2)
library(gridExtra)
library(mosaic)
library(dplyr)

options("pillar.sigfig" = 10) # print 10 significant digits in summarize output
```

A study was conducted to examine the effectiveness of four different hand-washing methods for eliminating bacteria.

```{r}
soap <- read_csv("https://raw.githubusercontent.com/marievozanne/marievozanne.github.io/master/stat242/datasets/soap.csv")
names(soap) <- c("bacterial_counts", "method")

soap %>%
  count(method)
```

#### 1. Make an appropriate plot of the data.

```{r}

```

#### 2. Conduct a test of the claim that all four methods are equally effective.

```{r}

```

#### 3. Conduct a test of the claim that the "Antibacterial Soap", "Soap", and "Water" methods are equally effective.

```{r}

```

#### 4. If you have extra time and want a refresher, calculate the mean and standard deviation of observations in each group.

```{r}

```
